True versus apparent shapes of astrophysical bow shocks

### 2017-07-06 papers/Paper1/sec-quadrics-observations.tex
Update description of Cox sources in text

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \includegraphics[trim=10 0 60 30, clip]{figs/cwleo-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/epaqr-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/khicyg-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/rtvir-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/waql-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/wpic-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/rscl-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/tetaps-imageplot}
  \caption{As Fig~\ref{fig:herschel-arc-fits}, but for a further 8
    Class~I sources from \citet{Cox:2012a} where the arc structure is
    more diffuse, weak, and/or asymmetric. For CW~Leo only (top-left),
    the right-hand panel shows a grayscale image of the \SI{160}{\um}
    rather than \SI{80}{\um} emission.}
  \label{fig:herschel-arc-fits-poor}
\end{figure*}

@@

We obtain a second sample of bow shocks from a far-infrared survey
\citep{Cox:2012a} of circumstellar shells around asymptotic giant
branch (AGB) stars and cool supergiants, obtained as part of the
\textit{Herschel} MESS (Mass-loss of Evolved StarS) program
\citep{Groenewegen:2011a}.  The survey sources were divided into four
classes, according to the overall shape of the extended emission at
\SI{70}{\um}: ``fermata~\textfermata'', or arcs (Class~I);
``eyes~\faEye'' (Class~II); ``rings~{\Large \(\odot\)}'' (Class~III), and
``irregular~\staveXXV'' (Class~IV).  Of these, only the Class~I
sources clearly correspond to bow shocks, which represent 23 out of 50
total sources detected with extended emission.  For our sample, we
select the 7 Class~I sources where the shape parameters can be
unambiguously measured, and which are shown in
Figure~\ref{fig:herschel-arc-fits}.  For some of the remaining Class~I
sources (Fig.~1 of \citealp{Cox:2012a}), the bow shock becomes too
diffuse around the ``sides'', so that \(R_{90}\) cannot be reliably
determined (examples include \(\theta\)~Aps and )

>>>>

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \includegraphics[trim=10 0 60 30, clip]{figs/cwleo-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/epaqr-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/khicyg-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/rtvir-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/waql-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/wpic-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/rscl-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/tetaps-imageplot}
  \caption{As Fig~\ref{fig:herschel-arc-fits}, but for a further 8
    Class~I sources from \citet{Cox:2012a} where the arc structure is
    more diffuse, weak, and/or asymmetric. For CW~Leo only (top-left),
    the right-hand panel shows a grayscale image of the \SI{160}{\um}
    rather than \SI{70}{\um} emission.}
  \label{fig:herschel-arc-fits-poor}
\end{figure*}

@@

We obtain a second sample of bow shocks from a far-infrared survey
\citep{Cox:2012a} of circumstellar shells around asymptotic giant
branch (AGB) stars and cool supergiants, obtained as part of the
\textit{Herschel} MESS (Mass-loss of Evolved StarS) program
\citep{Groenewegen:2011a}.  The survey sources were divided into four
classes by \citeauthor{Cox:2012a}, according to the overall shape of
the extended emission at \SI{70}{\um}: ``fermata~\textfermata'', or
arcs (Class~I); ``eyes~\faEye'' (Class~II); ``rings~{\Large
  \(\odot\)}'' (Class~III), and ``irregular~\staveXXV'' (Class~IV).  Of
these, only the Class~I sources clearly correspond to bow shocks,
which represent 22 out of 50 total sources detected with extended
emission.  For our sample, we select the 16 Class~I sources where the
shape parameters can be reliably measured, and which are shown in
Figures~\ref{fig:herschel-arc-fits}
and~\ref{fig:herschel-compare-mipsgal}.  In most sources, the bow
shock shell is most clearly visible in the \SI{70}{\um} band, with the
exception being CW~Leo where the \SI{180}{\um} band is used instead.

The remaining six Class~I sources (Fig.~1 of \citealp{Cox:2012a}) are
too asymmetrical or irregular to reliably determine \(R_{c}\) and
\(R_{90}\), and are therefore excluded from our sample.
